Constant-round Blind Classical Verification of Quantum Sampling

### 2020-07-31 qpip0.tex
Attempt to clean up discussions

Clearly $\PiSampZ$ is a $\QPIP_0$ protocol for $\SampBQP$ with negligible completeness error.
We now show that it is computationally sound.
\Ethan{Try to word the following a bit better}
The intuition is that the we run $m$ copies of the naive $\QPIP_0$ and do testing on randomly chosen $m-1$ copies of them, and do Hadamard round and calculate results from the remaining one copy. Therefore if the prover want to cheat, i.e. send something not binding in the Hadamard round copy, he would be caught with probability $1-1/m$. However, the prover might create correlations between copies that let him cheat with probability much higher than $1/m$. We are able to bound the soundness error as $O(1/\sqrt{m})$. To prove that, we use the following partition lemma from \cite{arXiv:ChiaChungYam19}, which intuitively says that for each $i\in[m]$, there exist two efficient ``projectors" \footnote{Actually they are not projectors, but for the simplicity of this discussion let's assume they are.} $G_{0,i}$ and $G_{1,i}$ in the prover's internal space with $G_{0,i}+G_{1,i} \approx Id$. $G_{0,i}$ represents the subspace that are rejected with high probability in the testing round of $i$-th copy, while $G_{1,i}$  represents the subspace accepted with high probability\footnote{This is also not technically correct as we will discuss later.} in the testing round of $i$-th copy.
Also as a careful reader might have noticed, the prover's space don't happen to split nicely into parts of very high accept probability in the testing round and parts with very low accept probability, as there will always be something in the middle. In \cite{arXiv:ChiaChungYam19} this is solved by doing eigenvalue estimation to calculate the accept probability, then split the space into parts that are accepted with probability higher or lower than a small threshold $\gamma$. However, states with accept probability really close to the threshold $\gamma$ can not be classified, so we need to average over randomly chosen $\gamma$ to have $G_{0,i}+G_{1,i} \approx Id$.

@@

\Ethan{The following discussion is under construction}

By using \Cref{lem:partition2} iteratively, we can decompose the prover's internal state.
Let $\ket{\psi}$ be the state the prover holds before he receives $\vec{c}$;
\Ethan{WLOG $\ket{\psi}$ is pure, or maybe can purify?}
we denote the corresponding Hilbert space as $H_{\regX,\regZ}$.
For all $k\leq m$, $d\in \zo^k$, $\gamma\in\set{\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}}$, and $\ket{\psi} \in H_{\regX,\regZ}$, define
$$\ket{\psi_{d,\gamma}}\defeq G_{d_k,k,\gamma}\ldots G_{d_2,2,\gamma} G_{d_1,1,\gamma} \ket{\psi}.$$
For example, $\ket{\psi_{110, \gamma}}$ intuitively corresponds to the component that would pass the first two copies' testing rounds and fail the third one.
At this point it is tempting to decompose $\ket{\psi}$ into $\ket{\psi_{s, \gamma}}$ where $s\in\zo^m$ and say that $\ket{\psi_{1^m, \gamma}}$ is the only component that is not rejected with high ($1-1/m$) probability;
however, $G_{1,i}$ don't commute with $G_{1,j}$, so $\ket{\psi_{1^m, \gamma}}$ is only binding for the $m$-th copy.
Instead, we must make a point-wise argument for each $i\in[m]$, then... \Ethan{TODO}

For all $i\in[m]$, we define
\begin{align} \label{eq:partition-string}
	\ket{\psi} =& \ket{\psi_{0,\gamma}}+\ket{\psi_{1,\gamma}}+\ket{\psi_{err,1,\gamma}} \nn \\
	=& \ket{\psi_{0,\gamma}}+\ket{\psi_{10,\gamma}}+\ket{\psi_{11,\gamma}}+\ket{\psi_{err,1,\gamma}}+\ket{\psi_{err,2,\gamma}} \nn \\
	=& \ket{\psi_{0,\gamma}}+\ket{\psi_{10,\gamma}}+\ket{\psi_{110,\gamma}}+\cdots+\ket{\psi_{1^{m-1}0,\gamma}}+\ket{\psi_{1^{m-1}1,\gamma}} \nn \\
	&+\ket{\psi_{err,1,\gamma}}+\ket{\psi_{err,2,\gamma}}+\cdots+\ket{\psi_{err,m,\gamma}} \nn\\
	=&\sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}} +\ket{\psi_{1^i,\gamma}} +\sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}}
\end{align}
where we abuse the notation and use $\ket{\psi_{err,i,\gamma}}$ to denote the error state we get from decomposing $\ket{\psi_{1^{i-1},\gamma}}$.

>>>>

Clearly $\PiSampZ$ is a $\QPIP_0$ protocol for $\SampBQP$ with negligible completeness error.
We now show that it is computationally sound.
We first use the following partition lemma from \cite{arXiv:ChiaChungYam19}, which intuitively says that for each $i\in[m]$, there exist two efficient ``projectors" \footnote{Actually they are not projectors, but for the simplicity of this discussion let's assume they are.} $G_{0,i}$ and $G_{1,i}$ in the prover's internal space with $G_{0,i}+G_{1,i} \approx Id$. $G_{0,i}$ represents the subspace that are rejected with high probability in the testing round of $i$-th copy, while $G_{1,i}$  represents the subspace accepted with high probability\footnote{This is also not technically correct as we will discuss later.} in the testing round of $i$-th copy.
Also as a careful reader might have noticed, the prover's space don't split nicely into parts of very high accept probability in the testing round and parts with very low accept probability, as there will always be something in the middle. In \cite{arXiv:ChiaChungYam19} this is solved by doing eigenvalue estimation \Ethan{Any better ways to describe this...?} to calculate the accept probability, then split the space into parts that are accepted with probability higher or lower than a small threshold $\gamma$. However, states with accept probability really close to the threshold $\gamma$ can not be classified, so we need to average over randomly chosen $\gamma$ to have $G_{0,i}+G_{1,i} \approx Id$.

@@

By using \Cref{lem:partition2} iteratively, we can decompose the prover's internal state.
Let $\ket{\psi}$ be the state the prover holds before he receives $\vec{c}$;
we denote the corresponding Hilbert space as $H_{\regX,\regZ}$.
For all $k\leq m$, $d\in \zo^k$, $\gamma\in\set{\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}}$, and $\ket{\psi} \in H_{\regX,\regZ}$, define
$$\ket{\psi_{d,\gamma}}\defeq G_{d_k,k,\gamma}\ldots G_{d_2,2,\gamma} G_{d_1,1,\gamma} \ket{\psi}.$$
For example, $\ket{\psi_{110, \gamma}}$ intuitively corresponds to the component that would pass the first two copies' testing rounds and fail the third one.
At this point it is tempting to decompose $\ket{\psi}$ into $\ket{\psi_{s, \gamma}}$ where $s\in\zo^m$,
and say that $\ket{\psi_{1^m, \gamma}}$ is the only component that is not rejected with high probability.
This doesn't work, however, as $G_{1,i}$ don't commute with $G_{1,j}$, so $\ket{\psi_{1^m, \gamma}}$ is only binding for the $m$-th copy.
Instead, we start with a pointwise argument and fix the Hadamard round on the $i$-th copy,
and show that the corresponding output is $O(\norm{\ket{\psi_{1^{i-1}0}}})$-close to ideal.
We can later average out this error over the different choices of $i$, since not all $\norm{\ket{\psi_{1^{i-1}0}}}$ can be large at the same time.
To begin, for all $i\in[m]$, we decompose $\ket{\psi}$ as follows:
\begin{align} \label{eq:partition-string}
	\ket{\psi} =& \ket{\psi_{0,\gamma}}+\ket{\psi_{1,\gamma}}+\ket{\psi_{err,1,\gamma}} \nn \\
	=& \ket{\psi_{0,\gamma}}+\ket{\psi_{10,\gamma}}+\ket{\psi_{11,\gamma}}+\ket{\psi_{err,1,\gamma}}+\ket{\psi_{err,2,\gamma}} \nn \\
	=& \ket{\psi_{0,\gamma}}+\ket{\psi_{10,\gamma}}+\ket{\psi_{110,\gamma}}+\cdots+\ket{\psi_{1^{m-1}0,\gamma}}+\ket{\psi_{1^{m-1}1,\gamma}} \nn \\
	&+\ket{\psi_{err,1,\gamma}}+\ket{\psi_{err,2,\gamma}}+\cdots+\ket{\psi_{err,m,\gamma}} \nn\\
	=&\sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}} +\ket{\psi_{1^i,\gamma}} +\sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}}
\end{align}
where we use $\ket{\psi_{err,i,\gamma}}$ to denote the error state we get from decomposing $\ket{\psi_{1^{i-1},\gamma}}$.
